\documentclass[conf]{new-aiaa}
%\documentclass[journal]{new-aiaa} for journal papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt} 

\title{Multidisciplinary Optimization of a Turboelectric Tiltwing Urban Air Mobility Aircraft}

\author{Eric S. Hendricks\footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11.}, Robert D. Falck\footnote{Aerospace Engineer, Mission Analysis and Architecture Branch, 21000 Brookpark Rd MS 162-2, AIAA Member.}, Justin S. Gray \footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11, AIAA Member}, Eliot D. Aretskin-Hariton\footnote{Aerospace Engineer, Intelligent Control and Autonomy Branch, 21000 Brookpark Rd MS 77-1.}, Daniel J. Ingraham \footnote{Aerospace Engineer, Acoustics Branch, 21000 Brookpark Rd MS 54-3}, \\ Jeffryes W. Chapman\footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11.}, Sydney L. Schnulo\footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11.}, Jeffrey C. Chin\footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11.}, John P. Jasa\footnote{Aerospace Engineer Intern, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11 and Ph.D. Candidate, University of Michigan.}, and Jennifer D. Bergeson\footnote{Aerospace Engineer Intern, Propulsion Systems Analysis Branch, 21000 Brookpark Rd MS 5-11 and Undergraduate Student, Purdue University.}}
\affil{NASA Glenn Research Center, Cleveland, OH, 44135}

\begin{document}

\maketitle



% Main point: Developing a new multidisciplinary approach/toolset for designing UAM vehicles which are highly coupled

% Baseline design process from Chris Silva and compare to our design process

% Focus on integration of disciplines and use of gradient-based optimization

% Demonstration problem summary and optimization formulation

% Demonstration problem results


% disciplines:
%   aerodynamics
%   structures/mass
%   propulsion (cycle/electrical/propeller)
%   trajectory
% 



\begin{abstract}
Urban air taxis, also known as urban air mobility (UAM) vehicles, are anticipated to be an area of significant market growth in the near future.  
These vehicles are typically vertical take-off and landing (VTOL) designs which are capable of carrying 1 to 30 passengers in an intra-urban environment with flights of less than 50 nautical miles. 
Development of UAM vehicles and their integration into the airspace will be enabled by advancements in a number of areas including electrified propulsion systems, structures, acoustics, automation, and controls.
However, creating optimized designs for these unique vehicles with emerging technologies across these disciplines presents a new challenge.
This work describes the development of a multidisciplinary analysis environment which can be used to support the conceptual design of these UAM vehicles.
The tools included in this multidisciplinary analysis model the aircraft trajectory, vehicle aerodynamics, structures,  and electrified propulsion system.  
The multidisciplinary analysis environment is then demonstrated in the design optimization of a turboelectric tiltwing UAM vehicle concept. 
\end{abstract}

% \section{Nomenclature}

% {\renewcommand\arraystretch{1.0}
% \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
% $A$  & amplitude of oscillation \\
% $a$ &    cylinder diameter \\
% $C_p$& pressure coefficient \\
% $Cx$ & force coefficient in the \textit{x} direction \\
% $Cy$ & force coefficient in the \textit{y} direction \\
% c   & chord \\
% d$t$ & time step \\
% $Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
% $Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
% $f, g$   & generic functions \\
% $h$  & height \\
% $i$  & time index during navigation \\
% $j$  & waypoint index \\
% $K$  & trailing-edge (TE) nondimensional angular deflection rate
% \end{longtable*}}

\section{Introduction}\label{sec:intro}
\input{intro} %Eric

\section{Traditional Design and Analysis Environment}\label{sec:trad_process}
\input{trad_process} %Justin

\section{Multidisciplinary Design, Analysis, and Optimization Environment}\label{sec:mdao_process}
\input{mdao_process_overview} %Eric, Rob, Justin, Eliot


\subsection{Propulsion System Analysis}
\input{propulsion} %Eric, Jeff, Dan

\subsection{Wing Aerodynamic and Structural Analysis}
\input{aero} %John, Justin? Eliot?

\subsection{Aircraft Mass Analysis}
\input{struct} %Bruce, Sydney, Jennifer? John? Justin? Eliot?

\subsection{Optimal Control and Trajectory Analysis}
\input{traj} %Rob

% Include thermal section if it makes it into the optimization
% \subsection{Thermal System Analysis}
% \input{thermal} %Jeff, Sydney

% Include accoustics section if it makes it into the optimization
% \subsection{Acoustic Analysis}
% \input{acoustics} %Dan

\section{Turbo-Electric Tiltwing Optimization Demonstration Problem}\label{sec:opt_prob}
\input{opt_problem} %Eric, Rob, Justin, Eliot

% \section{Turbo-Electric Tiltwing Optimization Demonstration Results}\label{sec:opt_results}
% \input{opt_results} %Eric, Rob, Justin, Eliot

\section{Conclusion and Future Work}\label{sec:conc}
\input{conclusions} %Eric, Rob, Justin 


\section*{Acknowledgments}
The work presented in this paper is supported by NASA's Transformative Tools and Technologies (TTT) Project.  

\bibliography{References}




\end{document}
