% This file should contain a short summary of the structures/mass analysis tool and models

In addition to the structural analysis completed for the wing, the disciplinary design phase includes additional calculations to estimate the overall mass of the aircraft.
This estimation is broken down by major aircraft subsystem with empirical correlations used to approximated the weight for the subsystems.

For the aircraft structure, empirical correlations were used following the method applied by NDARC\cite{NDARC}, which are often based on the U.S. Army Aeroflightdynamics Directorate (AFDD) preliminary design methods, with the exception of the wing weight which came from OpenAeroStruct.
First, the fuselage mass was based on the AFDD84 NDARC universal body weight model.
In addition, the tail weight was computed from the AFDD82 NDARC model and included the horizontal, vertical \textbf{and tail rotor components}.
Fuel system weight includes tanks and supporting structures, and is based on a 15 aircraft regression.
The landing gear and alighting structural masses were based on a regression of 28 aircraft.

For the propulsion system related elements, the mass estimating equations came from a more diverse set of 
The propeller weight was based on the NDARC AFDD82 model used 35 aircraft to empirically determine hub and blade weights. 
Next, the drive system weight including gearbox, rotor break, and shaft was included and is based on the NDARC AFDD83 regression based on 30 aircraft.
For the electric system, the motor, inverter, rectifier and generator weights are all estimated based on linear regressions of flightweight systems presently in development for aircraft systems.
For the electric cabling, an empirical regression based on the maximum current was used, with the max current set by a worst-case failure where several cables are severed. 
For the battery, the weight was estimated based on an assumed energy density and capacity of the battery, with 2 minutes of emergency hover power required.
Finally, the turboshaft engine weight was approximated using a linear regression based on shaft power for existing turboshaft engines.

Mass estimates are broken down and calculated in the following categories,
listed here by weight in descending order.
Convert this to a table??

\begin{itemize}

    \item engine  2055.6 lbs
    \item fuselage 1129.2 lbs
    \item wing 821.8 lbs
    \item motor 810.2 lbs
    \item drive system 715 lbs
        \begin{itemize}
            \item gearbox
        \end{itemize}
    \item fuel system 689.7 lbs
        \begin{itemize}
            \item battery
        \end{itemize}
    \item propellers 502.6 lbs
    \item landing gear 477.4 lbs
    \item cables 300 lbs
    \item tail 110.9 lbs
    \item inverter 75lbs
\end{itemize}



% bibtex
